---
title: "CDC2026"
author: "teamcrossword"
format: html
editor: visual
---

## Loading Data

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(tidymodels)
library(knitr)
library(car)
library(nnet)
library(yardstick)
library(pROC)
library(forcats)


#Loading csv
DepMus <- read.csv("C:/Users/Truman/Downloads/CDC2026 - Dep-_Mus_mxmh_survey_results.csv")

#Setting as factor so model can predict
DepMus$Fav.genre <- as.factor(DepMus$Fav.genre)

#setting training vs. testing data
set.seed(101)
sample_index <- sample(1:nrow(DepMus), size = floor(.85*nrow(DepMus)))

train_DepMus <- DepMus[sample_index,]
test_DepMus <- DepMus[-sample_index,]

```

## Initial Model

```{r}
#Fitting model with all variables

fit_DepMus <- multinom(Fav.genre~Age+Anxiety+Depression+Insomnia+OCD+Primary.streaming.service+Hours.per.day+Exploratory+Foreign.languages+Music.effects, train_DepMus)

tidy(fit_DepMus)|>
  kable(digits = 3)

```

## VIF Checking

```{r}
#have to use work around with multinom output not working, so using random model to compute VIF

aux_model<-lm(1:nrow(DepMus)~Age+Anxiety+Depression+Insomnia+OCD+Primary.streaming.service+Hours.per.day+Exploratory+Foreign.languages+Music.effects, DepMus)

vif(aux_model)
```

No Predict shows significant signs of collinearity

## Confusion Matrix of Initial Model

```{r}
#Making prediction column
test_DepMus$predict <- predict(fit_DepMus, newdata = test_DepMus)

confDepMus <- conf_mat(data= test_DepMus, truth=Fav.genre, estimate=predict)

autoplot(confDepMus, type="heatmap")


```

That's chopped, we're going to need to combine outputs.

## Combine

```{r}
#going to combine K-pop and Pop, Metal and Rock, Rap and Hip-Hop

mutDepMus <- DepMus |> 
                  mutate(Fav.genre = fct_collapse(Fav.genre, "Rock" = c("Rock", "Metal"), "Pop"=c("Pop","K pop"), "Hip hop" = c("Rap", "Hip hop")))


```

## New Confusion Matrix

```{r}


tidy(fit_mutDepMus)|>
  kable(digits = 3)

#Fixing Test Data and prediction

mut_train_DepMus <- mutDepMus[sample_index,]
mut_test_DepMus <- mutDepMus[-sample_index,]

#New Model
fit_mutDepMus <- multinom(Fav.genre~Age+Anxiety+Depression+Insomnia+OCD+Primary.streaming.service+Hours.per.day+Exploratory+Foreign.languages+Music.effects, mut_train_DepMus)

tidy(fit_mutDepMus)|>
  kable(digits = 3)


#Adding Prediction Var
mut_test_DepMus$predict <- predict(fit_mutDepMus, newdata = mut_test_DepMus)

#Confusion Matrix

confDepMus <- conf_mat(data= mut_test_DepMus, truth=Fav.genre, estimate=predict)

autoplot(confDepMus, type="heatmap")


```

```{r}
pred_obj <- predict(fit_mutDepMus,newdata = mut_test_DepMus[1,], type = "probs")

tidy(pred_obj) |>
  kable(digits=3)
```

Ok, pivoting towards finding what vars we can remove and then reweighting

Comparing BIC of just the 4 OCD, Anxiety, Depression, Insomnia and then adding vars

```{r}
fit_mutDepMus1 <- multinom(Fav.genre~Age+Anxiety+Depression+Insomnia+OCD, mut_train_DepMus)

fit_mutDepMus2 <- multinom(Fav.genre~Age+Anxiety+Depression+Insomnia+OCD+Primary.streaming.service, mut_train_DepMus)

fit_mutDepMus3 <- multinom(Fav.genre~Age+Anxiety+Depression+Insomnia+OCD+Primary.streaming.service+Hours.per.day, mut_train_DepMus)

fit_mutDepMus4 <- multinom(Fav.genre~Age+Anxiety+Depression+Insomnia+OCD+Primary.streaming.service+Hours.per.day+Exploratory, mut_train_DepMus)


AIC(fit_mutDepMus, fit_mutDepMus1, fit_mutDepMus2, fit_mutDepMus3, fit_mutDepMus4)


```

Hmm, they're basically all similar, but what if I re-weight?

```{r}
#thanks claude

class_counts <- table(mut_train_DepMus$Fav.genre)
inv_freq <- 1 / class_counts  # base weights, higher for rarer classes

strengths <- c(0, 0.5, 1, 1.5, 2)  # 0 = no reweighting, higher = more aggressive
results <- data.frame(strength = strengths, brier = NA)

for (i in seq_along(strengths)) {
  s <- strengths[i]
  
  w_lookup <- inv_freq^s
  w_lookup <- w_lookup / mean(w_lookup)  # normalize so weights average to 1
  
  mut_train_DepMus$w <- w_lookup[mut_train_DepMus$Fav.genre]
  
  model <- multinom(Fav.genre ~ Age+Anxiety+Depression+Insomnia+OCD+Primary.streaming.service, data = mut_train_DepMus, weights = mut_test_DepMus$w, trace = FALSE)
  probs <- predict(model, newdata = mut_test_DepMus, type = "probs")
  
  y_matrix <- model.matrix(~ Fav.genre - 1, data = mut_test_DepMus)
  colnames(y_matrix) <- levels(mut_test_DepMus$Fav.genre)
  y_matrix <- y_matrix[, colnames(probs)]
  
  results$brier[i] <- mean(rowSums((probs - y_matrix)^2))
}

results
best_strength <- results$strength[which.min(results$brier)]
best_strength

table(mut_train_DepMus$Fav.genre, mut_train_DepMus$w)
```

```{r}
table(mut_train_DepMus$Fav.genre, mut_train_DepMus$w) |> kable(digits=2)
```

Screw it here's our model:

## Model

```{r}
fit_mutDepMus2|>
  tidy()|>  
    select(y.level, term, estimate, p.value) |>
      kable(digits=3)
```
